---
title: 'parental migration and adolescents educational performance'
output: html_notebook
---

Load packages
```{r}
library(tidyverse) 
library(haven)
library(fixest)
library(modelsummary)
```

## Data cleaning
Read CEPS data
```{r}
d_stu1 <- read_dta('cepsw1studentCN.dta') #wave 1 student
d_stu2 <- read_dta('cepsw2studentCN.dta') #wave 2 student
d_par1 <- read_dta('cepsw1parentCN.dta') #wave 1 parent
d_par2 <- read_dta('cepsw2parentCN.dta') #wave 2 parent
```

Remove wave 1's observations of grade 9; they were not followed up in wave 2
```{r}
d_stu1 <- d_stu1 %>% 
  subset(grade9==0) %>% 
  select(!c(frame, subsample, sweight, grade9))
d_stu2 <- d_stu2 %>% 
  select(!c(w2frame, w2subsample, w2sweight, w1w2sweight))
d_par1 <- d_par1 %>% 
  subset(grade9==0) %>% 
  select(!c(frame, subsample, grade9))
```

Assemble a panel dataset in wide format
```{r}
d_1 <- d_stu1 %>% left_join(d_par1, by=c('ids', 'clsids', 'schids', 'ctyids', 'fall')) 
d_2 <- d_stu2 %>% left_join(d_par2, by=c('ids', 'clsids', 'w2clsids', 'schids', 'ctyids', 'w2fall'))
d <- d_1 %>% right_join(d_2, by=c('ids', 'clsids', 'schids', 'ctyids'))
```

```{r}
d <- d %>% mutate(
  age = 2013 - a02a, #student's age at baseline
  local.resi = age - a07 #years of residence at the current county
)
```

Compute standardized exam grades (within-school z-scores)
```{r}
d <- d %>% #Total exam grades at wave 1 and at wave 2
  mutate(w1ttl = tr_chn + tr_mat + tr_eng, 
         w2ttl = w2chn + w2mat + w2eng) 
d <- d %>% #Within-school z-scores for Chinese, math, English exams and their total, respectively
  group_by(schids) %>%
  mutate(w1chn_std = as.numeric(scale(tr_chn)),
         w1mat_std = as.numeric(scale(tr_mat)),
         w1eng_std = as.numeric(scale(tr_eng)),
         w1ttl_std = as.numeric(scale(w1ttl)),
         w2chn_std = as.numeric(scale(w2chn)),
         w2mat_std = as.numeric(scale(w2mat)),
         w2eng_std = as.numeric(scale(w2eng)),
         w2ttl_std = as.numeric(scale(w2ttl))
         ) %>% ungroup()
```

Sample
```{r}
d_cl <- d %>% 
  filter(w2a0801==1) %>% #parents who are married (and alive)
  filter(be1201==1 & be1202==1) %>% #both parents live with children at baseline
  filter(local.resi>=6) #having stayed in the current county for at least six years (duration of primary school) before baseline
```

## Variables 
Dependent variables: Outcome differences between wave 2 and wave 1
```{r}
d_cl <- d_cl %>% mutate(
  chn_std = w2chn_std - w1chn_std,
  mat_std = w2mat_std - w1mat_std,
  eng_std = w2eng_std - w1eng_std,
  ttl_std = w2ttl_std - w1ttl_std,
  cog = w2cog3pl - cog3pl #Cognitive test score, standardized
) %>%
  drop_na(cog, chn_std, mat_std, eng_std, ttl_std)
```

Control variables
```{r}
d_cl <- d_cl %>% mutate(
         ch.girl = if_else(a01 == 2, 1, 0), #student is girl
         ch.rural = if_else(bd05 == 1, 1, 0), #student holds rural (agricultural) hukou
         ch.only.child = if_else(b01 == 1, 1, 0), #student is only child
         ch.boarding = if_else(c18 == 1, 1, 0), #student is boarding at school
         ch.ethn.minority = if_else(a03 != 1, 1, 0), #student is ethnic minority
         ch.health = a17, #student's self-reported health
         par.edu = if_else(b06 > b07, b06, b07), #Among two parents, the best-educated one's educational level
         #fa.edu = b07,
         #mo.edu = b06,
         home.internet = if_else(b13 == 2, 1, 0), #student has internet access at home
         home.book = b12 #Amount of book at home, student self-rated 
) %>% drop_na(
  ch.girl, ch.rural, ch.health, ch.only.child, ch.boarding, ch.ethn.minority, ch.health, par.edu, home.internet, home.book)
```

```
d_cl <- d_cl %>% mutate_at(c('b0201', 'b0202', 'b0203', 'b0204'), ~replace(., ch.na(.), 0))
d_cl <- d_cl %>% mutate(sibling = if_else(b01 == 1, 0, b0201 + b0202 + b0203 + b0204)) %>% #number of siblings
  drop_na(sibling)
```

Best-educated parent's years of education
```{r}
d_cl <- d_cl %>% mutate(par.edu.year = NA)
d_cl$par.edu.year[d_cl$par.edu == 1] <- 0
d_cl$par.edu.year[d_cl$par.edu == 2] <- 6
d_cl$par.edu.year[d_cl$par.edu == 3] <- 9
d_cl$par.edu.year[d_cl$par.edu == 4|d_cl$par.edu == 5|d_cl$par.edu == 6] <- 12
d_cl$par.edu.year[d_cl$par.edu == 7] <- 15
d_cl$par.edu.year[d_cl$par.edu == 8] <- 16
d_cl$par.edu.year[d_cl$par.edu == 9] <- 19
```

```
d_cl <- d_cl %>% mutate(fa.edu.year = NA)
d_cl$fa.edu.year[d_cl$fa.edu == 1] <- 0
d_cl$fa.edu.year[d_cl$fa.edu == 2] <- 6
d_cl$fa.edu.year[d_cl$fa.edu == 3] <- 9
d_cl$fa.edu.year[d_cl$fa.edu == 4|d_cl$fa.edu == 5|d_cl$fa.edu == 6] <- 12
d_cl$fa.edu.year[d_cl$fa.edu == 7] <- 15
d_cl$fa.edu.year[d_cl$fa.edu == 8] <- 16
d_cl$fa.edu.year[d_cl$fa.edu == 9] <- 19
```

```
d_cl <- d_cl %>% mutate(mo.edu.year = NA)
d_cl$mo.edu.year[d_cl$mo.edu == 1] <- 0
d_cl$mo.edu.year[d_cl$mo.edu == 2] <- 6
d_cl$mo.edu.year[d_cl$mo.edu == 3] <- 9
d_cl$mo.edu.year[d_cl$mo.edu == 4|d_cl$mo.edu == 5|d_cl$mo.edu == 6] <- 12
d_cl$mo.edu.year[d_cl$mo.edu == 7] <- 15
d_cl$mo.edu.year[d_cl$mo.edu == 8] <- 16
d_cl$mo.edu.year[d_cl$mo.edu == 9] <- 19
```


## Treatment groups
At least one parent migrated (Control group as no parent migrated)
```{r}
d_cl <- d_cl %>% mutate(
  migr = if_else((w2ba0201==0 | w2ba0202==0), 1, 0), #Any parent became absent from household between baseline and endline survey
  migr_fa_only = NA,
  migr_fa = NA,
  migr_mo_only = NA,
  migr_mo = NA,
  migr_both = NA
  )
```

Only mother migrated
```{r}
d_cl$migr_mo_only[d_cl$migr == 0] <- 0
d_cl$migr_mo_only[d_cl$w2ba0201==1 & d_cl$w2ba0202==0] <- 1 
```

Mother migrated
```{r}
d_cl$migr_mo[d_cl$migr == 0] <- 0
d_cl$migr_mo[d_cl$w2ba0202==0] <- 1
```

Only father migrated
```{r}
d_cl$migr_fa_only[d_cl$migr == 0] <- 0
d_cl$migr_fa_only[d_cl$w2ba0201==0 & d_cl$w2ba0202==1] <- 1 
```

Father migrated
```{r}
d_cl$migr_fa[d_cl$migr == 0] <- 0
d_cl$migr_fa[d_cl$w2ba0201==0] <- 1
```

Both parents migrated
```{r}
d_cl$migr_both[d_cl$migr == 0] <- 0
d_cl$migr_both[d_cl$w2ba0201==0 & d_cl$w2ba0202==0] <- 1
```

## Descriptive statistics
```{r}
des_gender <- d_cl %>% count(ch.girl)
des_rural <- d_cl %>% count(ch.rural)
#des_sibling <- d_cl %>% group_by(sibling) %>% count
des_boarding <- d_cl %>% count(ch.boarding)
des_book <- d_cl %>% group_by(home.book) %>% count
des_internet <- d_cl %>% group_by(home.internet) %>% count
des_par.edu.year <- d_cl %>% group_by(par.edu.year) %>% count
des_ethn.minority <- d_cl %>% group_by(ch.ethn.minority) %>% count
des_gender
des_rural
#des_sibling
des_boarding
des_par.edu.year
des_book
des_internet
des_ethn.minority
```


### Wave 2 outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

### Change in outcomes of treatment group vs control group
```{r}
d_cl %>%
  group_by(migr) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo_only) %>% 
  summarise(n_cases = n(),
            mean_cog = mean(w2cog3pl, na.rm=T),
            mean_ttl = mean(w2ttl_std, na.rm=T),
            mean_chn = mean(w2chn_std, na.rm=T),
            mean_mat = mean(w2mat_std, na.rm=T),
            mean_eng = mean(w2eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_mo) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa_only) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_fa) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

```{r}
d_cl %>%
  group_by(migr_both) %>% 
  summarise(n_cases = n(),
            mean_change_cog = mean(cog, na.rm=T),
            mean_change_ttl = mean(ttl_std, na.rm=T),
            mean_change_chn = mean(chn_std, na.rm=T),
            mean_change_mat = mean(mat_std, na.rm=T),
            mean_change_eng = mean(eng_std, na.rm=T)
            ) %>%
  drop_na()
```

## DID basic
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
For student i in school s, $$\Delta score_{i,s}$$ is the change in standardized test score between baseline survey and endline survey, $$migr_{i,s}$$ is the treatment dummy variable, and $$FE_{s}$$ is the school-level fixed effect.

Regressing on cognitive test score (standardized)
```{r}
did_cog <- feols(cog ~ migr | schids, data = d_cl) 
did_cog_m_only <- feols(cog ~ migr_mo_only | schids, data = d_cl) 
did_cog_m <- feols(cog ~ migr_mo | schids, data = d_cl) 
did_cog_f_only <- feols(cog ~ migr_fa_only | schids, data = d_cl) 
did_cog_f <- feols(cog ~ migr_fa | schids, data = d_cl) 
did_cog_both <- feols(cog ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_cog <- list(
did_cog,
did_cog_m_only,
did_cog_m,
did_cog_f_only,
did_cog_f,
did_cog_both) 
models_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on total exam score
```{r}
did_ttl <- feols(ttl_std ~ migr | schids, data = d_cl) 
did_ttl_m_only <- feols(ttl_std ~ migr_mo_only | schids, data = d_cl) 
did_ttl_m <- feols(ttl_std ~ migr_mo | schids, data = d_cl) 
did_ttl_f <- feols(ttl_std ~ migr_fa | schids, data = d_cl) 
did_ttl_f_only <- feols(ttl_std ~ migr_fa_only | schids, data = d_cl) 
did_ttl_both <- feols(ttl_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_ttl <- list(
did_ttl,
did_ttl_m_only,
did_ttl_m,
did_ttl_f_only,
did_ttl_f,
did_ttl_both) 
models_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_chn <- feols(chn_std ~ migr | schids, data = d_cl) 
did_chn_m_only <- feols(chn_std ~ migr_mo_only | schids, data = d_cl) 
did_chn_m <- feols(chn_std ~ migr_mo | schids, data = d_cl) 
did_chn_f_only <- feols(chn_std ~ migr_fa_only | schids, data = d_cl) 
did_chn_f <- feols(chn_std ~ migr_fa | schids, data = d_cl) 
did_chn_both <- feols(chn_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_chn <- list(
did_chn,
did_chn_m_only,
did_chn_m,
did_chn_f_only,
did_chn_f,
did_chn_both) 
models_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Math score
```{r}
did_mat <- feols(mat_std ~ migr | schids, data = d_cl) 
did_mat_m_only <- feols(mat_std ~ migr_mo_only | schids, data = d_cl) 
did_mat_m <- feols(mat_std ~ migr_mo | schids, data = d_cl) 
did_mat_f_only <- feols(mat_std ~ migr_fa_only | schids, data = d_cl) 
did_mat_f <- feols(mat_std ~ migr_fa | schids, data = d_cl) 
did_mat_both <- feols(mat_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_mat <- list(
did_mat,
did_mat_m_only,
did_mat_m,
did_mat_f_only,
did_mat_f,
did_mat_both) 
models_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on English score
```{r}
did_eng <- feols(eng_std ~ migr | schids, data = d_cl) 
did_eng_m <- feols(eng_std ~ migr_mo | schids, data = d_cl)
did_eng_m_only <- feols(eng_std ~ migr_mo_only | schids, data = d_cl) 
did_eng_f <- feols(eng_std ~ migr_fa | schids, data = d_cl) 
did_eng_f_only <- feols(eng_std ~ migr_fa_only | schids, data = d_cl) 
did_eng_both <- feols(eng_std ~ migr_both | schids, data = d_cl)
```

Results
```{r}
models_eng <- list(
did_eng,
did_eng_m_only,
did_eng_m,
did_eng_f_only,
did_eng_f,
did_eng_both) 
models_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

## DID unrestricted
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \lambda \cdot score_{i,s;base} + \gamma \cdot FE_{s} + \varepsilon_{i,s} $$
where baseline score is a variable on right hand side

Regressing on cognitive test score (standardized)
```{r}
did_unres_cog <- feols(cog ~ migr + cog3pl | schids, data = d_cl) 
did_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl | schids, data = d_cl) 
did_unres_cog_m <- feols(cog ~ migr_mo + cog3pl | schids, data = d_cl) 
did_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl | schids, data = d_cl) 
did_unres_cog_f <- feols(cog ~ migr_fa + cog3pl | schids, data = d_cl) 
did_unres_cog_both <- feols(cog ~ migr_both + cog3pl | schids, data = d_cl)
```

Results
```{r}
models_unres_cog <- list(
did_unres_cog,
did_unres_cog_m_only,
did_unres_cog_m,
did_unres_cog_f_only,
did_unres_cog_f,
did_unres_cog_both) 
models_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on total exam score
```{r}
did_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std | schids, data = d_cl) 
did_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std | schids, data = d_cl)
```

Results
```{r}
models_unres_ttl <- list(
did_unres_ttl,
did_unres_ttl_m_only,
did_unres_ttl_m,
did_unres_ttl_f_only,
did_unres_ttl_f,
did_unres_ttl_both) 
models_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_unres_chn <- feols(chn_std ~ migr + w1chn_std | schids, data = d_cl) 
did_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std | schids, data = d_cl) 
did_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std | schids, data = d_cl) 
did_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std | schids, data = d_cl) 
did_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std | schids, data = d_cl) 
did_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std | schids, data = d_cl)
```

Results
```{r}
models_unres_chn <- list(
did_unres_chn,
did_unres_chn_m_only,
did_unres_chn_m,
did_unres_chn_f_only,
did_unres_chn_f,
did_unres_chn_both) 
models_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Math score
```{r}
did_unres_mat <- feols(mat_std ~ migr + w1mat_std | schids, data = d_cl) 
did_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std | schids, data = d_cl) 
did_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std | schids, data = d_cl) 
did_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std | schids, data = d_cl) 
did_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std | schids, data = d_cl) 
did_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std | schids, data = d_cl)
```

Results
```{r}
models_unres_mat <- list(
did_unres_mat,
did_unres_mat_m_only,
did_unres_mat_m,
did_unres_mat_f_only,
did_unres_mat_f,
did_unres_mat_both) 
models_unres_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on English score
```{r}
did_unres_eng <- feols(eng_std ~ migr + w1eng_std | schids, data = d_cl) 
did_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std | schids, data = d_cl)
did_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std | schids, data = d_cl) 
did_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std | schids, data = d_cl) 
did_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std | schids, data = d_cl) 
did_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std | schids, data = d_cl)
```

Results
```{r}
models_unres_eng <- list(
did_unres_eng,
did_unres_eng_m_only,
did_unres_eng_m,
did_unres_eng_f_only,
did_unres_eng_f,
did_unres_eng_both) 
models_unres_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```


## DID adjusted
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$
$$X_{i,s}$$ denotes a vector of covariates about the characteristics of students, parents, and households.

Regressing on cognitive test score (standardized)
```{r}
did_adj_cog <- feols(cog ~ migr  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m_only <- feols(cog ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_m <- feols(cog ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f_only <- feols(cog ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_f <- feols(cog ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_cog_both <- feols(cog ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_cog <- list(
did_adj_cog,
did_adj_cog_m_only,
did_adj_cog_m,
did_adj_cog_f_only,
did_adj_cog_f,
did_adj_cog_both) 
models_adj_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on total exam score
```{r}
did_adj_ttl <- feols(ttl_std ~ migr   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m_only <- feols(ttl_std ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_m <- feols(ttl_std ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f <- feols(ttl_std ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_f_only <- feols(ttl_std ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_ttl_both <- feols(ttl_std ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_ttl <- list(
did_adj_ttl,
did_adj_ttl_m_only,
did_adj_ttl_m,
did_adj_ttl_f_only,
did_adj_ttl_f,
did_adj_ttl_both) 
models_adj_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_adj_chn <- feols(chn_std ~ migr   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m_only <- feols(chn_std ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_m <- feols(chn_std ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f_only <- feols(chn_std ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_f <- feols(chn_std ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_chn_both <- feols(chn_std ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_chn <- list(
did_adj_chn,
did_adj_chn_m_only,
did_adj_chn_m,
did_adj_chn_f_only,
did_adj_chn_f,
did_adj_chn_both) 
models_adj_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Math score
```{r}
did_adj_mat <- feols(mat_std ~ migr   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m_only <- feols(mat_std ~ migr_mo_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_m <- feols(mat_std ~ migr_mo   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f_only <- feols(mat_std ~ migr_fa_only   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_f <- feols(mat_std ~ migr_fa   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_mat_both <- feols(mat_std ~ migr_both   + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_mat <- list(
did_adj_mat,
did_adj_mat_m_only,
did_adj_mat_m,
did_adj_mat_f_only,
did_adj_mat_f,
did_adj_mat_both) 
models_adj_mat %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on English score
```{r}
did_adj_eng <- feols(eng_std ~ migr  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_m <- feols(eng_std ~ migr_mo  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_eng_m_only <- feols(eng_std ~ migr_mo_only  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f <- feols(eng_std ~ migr_fa  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_f_only <- feols(eng_std ~ migr_fa_only  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_eng_both <- feols(eng_std ~ migr_both  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```

Results
```{r}
models_adj_eng <- list(
did_adj_eng,
did_adj_eng_m_only,
did_adj_eng_m,
did_adj_eng_f_only,
did_adj_eng_f,
did_adj_eng_both) 
models_adj_eng %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```


## DID adjusted unrestricted
$$\Delta score_{i,s} = \alpha + \beta \cdot migr_{i,s} + \gamma \cdot FE_{s} + \lambda \cdot score_{i,s;base} + \theta \cdot X_{i,s} + \varepsilon_{i,s}$$

Regressing on cognitive test score (standardized)
```{r}
did_adj_unres_cog <- feols(cog ~ migr + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m_only <- feols(cog ~ migr_mo_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_m <- feols(cog ~ migr_mo + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f_only <- feols(cog ~ migr_fa_only + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_f <- feols(cog ~ migr_fa + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_cog_both <- feols(cog ~ migr_both + cog3pl  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_cog <- list(
did_adj_unres_cog,
did_adj_unres_cog_m_only,
did_adj_unres_cog_m,
did_adj_unres_cog_f_only,
did_adj_unres_cog_f,
did_adj_unres_cog_both) 
models_adj_unres_cog %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```
Regressing on total exam score
```{r}
did_adj_unres_ttl <- feols(ttl_std ~ migr + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m_only <- feols(ttl_std ~ migr_mo_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_m <- feols(ttl_std ~ migr_mo + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f <- feols(ttl_std ~ migr_fa + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_f_only <- feols(ttl_std ~ migr_fa_only + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_ttl_both <- feols(ttl_std ~ migr_both + w1ttl_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_ttl <- list(
did_adj_unres_ttl,
did_adj_unres_ttl_m_only,
did_adj_unres_ttl_m,
did_adj_unres_ttl_f_only,
did_adj_unres_ttl_f,
did_adj_unres_ttl_both) 
models_adj_unres_ttl %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Chinese exam score
```{r}
did_adj_unres_chn <- feols(chn_std ~ migr + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m_only <- feols(chn_std ~ migr_mo_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_m <- feols(chn_std ~ migr_mo + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f_only <- feols(chn_std ~ migr_fa_only + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_f <- feols(chn_std ~ migr_fa + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_chn_both <- feols(chn_std ~ migr_both + w1chn_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_chn <- list(
did_adj_unres_chn,
did_adj_unres_chn_m_only,
did_adj_unres_chn_m,
did_adj_unres_chn_f_only,
did_adj_unres_chn_f,
did_adj_unres_chn_both) 
models_adj_unres_chn %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on Math score
```{r}
did_adj_unres_mat <- feols(mat_std ~ migr + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m_only <- feols(mat_std ~ migr_mo_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_m <- feols(mat_std ~ migr_mo + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f_only <- feols(mat_std ~ migr_fa_only + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_f <- feols(mat_std ~ migr_fa + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_mat_both <- feols(mat_std ~ migr_both + w1mat_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_mat_adj_unres <- list(
did_adj_unres_mat,
did_adj_unres_mat_m_only,
did_adj_unres_mat_m,
did_adj_unres_mat_f_only,
did_adj_unres_mat_f,
did_adj_unres_mat_both) 
models_mat_adj_unres %>% msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

Regressing on English score
```{r}
did_adj_unres_eng <- feols(eng_std ~ migr + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_m <- feols(eng_std ~ migr_mo + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
did_adj_unres_eng_m_only <- feols(eng_std ~ migr_mo_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_f <- feols(eng_std ~ migr_fa + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_f_only <- feols(eng_std ~ migr_fa_only + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl) 
did_adj_unres_eng_both <- feols(eng_std ~ migr_both + w1eng_std  + age + ch.girl + ch.health + ch.rural + ch.only.child +  ch.boarding + ch.ethn.minority + par.edu.year + home.book + home.internet | schids, data = d_cl)
```
Results
```{r}
models_adj_unres_eng <- list(
did_adj_unres_eng,
did_adj_unres_eng_m_only,
did_adj_unres_eng_m,
did_adj_unres_eng_f,
did_adj_unres_eng_f_only,
did_adj_unres_eng_both) 
models_adj_unres_eng %>% 
  msummary(stars = c('*' = .05, '**' = .01, '***' = .001), coef_rename =  c("migr" = "Explanator", "migr_mo_only" = "Explanator", "migr_mo" = "Explanator", "migr_fa" = "Explanator", "migr_fa_only" = "Explanator", "migr_both" = "Explanator"))
```

